Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-06-11 manuscript/manuscript.Rmd
updates for sensitivity figure

```{r figure_1, dependson="plot-options", fig.cap="Sensitivity of equilibrium cover to removal of climate effects from each vital rate regression.", fig.width=4.5, fig.height=6, cache=FALSE, results='hide'}
setwd("../montana/ipm/simulations/sensitivity_results/")
files <- list.files()
cover_files <- files[grep("cover", files)]
spp_id <- substr(cover_files, 1, 4)
clim_id <- rep(c("allClim", "Ppt", "ZPptTemp", "Temp",
                 "Ppt", "ZPptTemp", "Temp", 
                 "Ppt", "ZPptTemp","Temp"), 4)
vital_id <- rep(c("All", "Growth", "Growth", "Growth",
                  "Survival", "Survival", "Survival",
                  "Recruitment", "Recruitment", "Recruitment"), 4)
num_files <- length(cover_files)
all_sims <- data.frame(time=NA, cover=NA, species=NA, sim=NA, vital=NA)
for(i in 1:num_files){
  tmp <- read.csv(cover_files[i])
  tmp$species <- rep(spp_id[i], nrow(tmp))
  tmp$sim <- rep(clim_id[i], nrow(tmp))
  tmp$vital <- rep(vital_id[i], nrow(tmp))
  all_sims <- rbind(all_sims, tmp)
}
all_sims <- all_sims[2:nrow(all_sims),]
all_clim_sims <- subset(all_sims, vital=="All")

>>>>

```{r figure_1, dependson="plot-options", fig.cap="Sensitivity of equilibrium cover to removal of climate effects from each vital rate regression.", fig.width=4.5, fig.height=6, cache=FALSE, results='hide'}
setwd("../montana/ipm/simulations/sensitivity_results/")
files <- list.files()
cover_files <- files[grep("cover", files)]
spp_id <- substr(cover_files, 1, 4)
# clim_id <-substr(cover_files, 16, )
# clim_id <- rep(c("Ppt", "PptTemp", "Temp",
#                  "Ppt", "ZPptTemp", "Temp", 
#                  "Ppt", "ZPptTemp","Temp"), 4)
# vital_id <- rep(c("All", "Growth", "Growth", "Growth",
#                   "Survival", "Survival", "Survival",
#                   "Recruitment", "Recruitment", "Recruitment"), 4)
num_files <- length(cover_files)
all_sims <- data.frame(time=NA, cover=NA, species=NA, sim=NA, vital=NA)
for(i in 1:num_files){
  tmp <- read.csv(cover_files[i])
  tmpid <- substr(cover_files[i], 16, nchar(cover_files[i])-4)
  tmpid <- strsplit(tmpid, "(?!^)(?=[[:upper:]])", perl=T)
  if(length(tmpid[[1]])==3){
    ttt <- paste(tmpid[[1]][[1]], tmpid[[1]][[2]], sep="")
    tmpid[[1]] <- c(ttt, tmpid[[1]][3])
  }
  tmp$species <- rep(spp_id[i], nrow(tmp))
  tmp$sim <- rep(tmpid[[1]][2], nrow(tmp))
  tmp$vital <- rep(tmpid[[1]][1], nrow(tmp))
  all_sims <- rbind(all_sims, tmp)
}
all_sims <- all_sims[2:nrow(all_sims),]
all_clim_sims <- subset(all_sims, vital=="All")
